\documentclass[a4paper,11pt]{article}
\setlength{\textwidth}{15.93cm} \setlength{\textheight}{24.61cm}
\oddsidemargin=-0.0cm \topmargin=-1.33cm

\usepackage{charter,eulervm}
\renewcommand{\baselinestretch}{1.1}
\usepackage{amsthm,amsmath,amssymb,upgreek,marvosym}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{paralist}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames]{color}
\usepackage[pdftex,breaklinks,colorlinks,
    citecolor={blue}, linkcolor={blue},urlcolor=Maroon]{hyperref}
\usepackage{tkz-graph}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing,positioning, fit, calc}

\graphicspath{{./images/}}%helpful if your graphic files are in another directory
%
\theoremstyle{plain} %remark,  plain
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}{Definition}
\def\boxit#1{\vbox{\hrule\hbox{\vrule\kern4pt
  \vbox{\kern1pt#1\kern1pt}
\kern2pt\vrule}\hrule}}

\newcommand{\keywords}[1]{\bigskip \par\noindent
{\small{\em Keywords\/}: #1}}
\newcommand{\opt}[2]{\ensuremath{{\mathtt{#1}(#2)}}}
\newcommand{\comment}[1]{\`$\setminus\!\!\setminus${\em #1}}

\title{\vspace{6cm} COMP3335 Database Security Project Report}
\author{Masamichi Tanaka \\
		Xiating Ouyang  14111773D \\
		Yiran Wei 15063347D  \\
		Derek Mingyu Ma 14110563D \\
		Kuo-hao Fu \\
		Yuchen Yao 
}
\date{}

\begin{document}
\maketitle	
\newpage
\tableofcontents
\newpage

\section{Business background}
	Our website aims to provide some information about the courses provided by the University. Students who would like to take some courses might want to search on our websites for finding some information provided by the studnets who took the courses previously. For each course, we would let the students leave some comments for course materials and the professors. However, only the registered users can provide information for the subjects and see the information provided by other users. Therefore, for the visitors, they can only search for course code or course name to see whether there are some information about this course.

\section{Database design}
% xiating

\subsection{Entity-relation diagram}
% yiran

\subsection{Table schema}
% xiating

\section{Functional requirement}
	1. Each user can successfully register, log in and log out an account.
	2. Each user can leave comments for the courses and search for the course information provided by other users.
	3. Each user can search the course information by using the course code, course name, department code or by messages provided by others. 
	4. Only the admin can create course information.
	5. The visitors of the websites can only view the course name or course code that are created. 

\section{Security policies and enforcement}

\subsection{Security requirement}


\subsection{Security mechanism}



\section{Contributions}
 % xiating

\section{Checklist of features}
 

\section{Testing URL}
Please test our project at \url{http://128.199.130.241/}.

\bibliographystyle{unsrt}
\bibliography{report}


\end{document}